A Standardized Effect Size for Evaluating the Comparing the Strength of Phylogenetic Signal

### 2020-07-15 Manuscript/OldVsns/Manuscript-6.Rmd
pnas vsn

Macroevolutionary studies frequently characterize the phylogenetic signal in phenotypes, and wish to compare the strength of that signal across traits. However, analytical tools for such comparisons have largely remained underdeveloped. In this study, we evaluated the efficacy of one commonly used parameter (Pagel's $\lambda$) to estimate the strength of phylogenetic signal in phenotypic traits, and evaluate the degree to which $\lambda$ correctly identifies known levels of phylogenetic signal. We find that the precision of $\lambda$ in estimating actual levels of phylogenetic signal is often inaccurate, and that biological interpretations of the strength of phylogenetic signal based on $\lambda$ are therefore compromised. We then propose a standardized effect size based on $Kappa$ ($Z_K$), which measures the strength of phylogenetic signal, and places it on a common scale for statistical comparison. Tests based on $Z_K$ provide a mechanism for formally comparing the strength of phylogenetic signal across datasets, in much the same manner as effect sizes may be used to summarize patterns in quantitative meta-analysis. Our approach extends the phylogenetic comparative toolkit to address hypotheses that compare the strength of phylogenetic signal various phenotypic traits, even when those traits are found in different evolutionary lineages or of in different units or scale.

@@

# Introduction
Investigating macroevolutionary patterns of trait variation requires a phylogenetic perspective, because the shared ancestry among species generates statistical non-independence [@Felsenstein1985; @HarveyPagel1991]. Accounting for this evolutionary non-independence is the purview of *phylogenetic comparative methods* (PCMs); a suite of analytical tools that condition the data on the phylogeny through the course of statisical evaluations of phenotypic trends [e.g., @Grafen1989; @GarlandIves2000; @Rohlf2001; @ButlerKing2004]. The past several decades have witnessed a rapid expansion in the development of PCMs to address an ever-growing set of macroevolutionary hypotheses [@MartinsHansen1997; @OMeara_et_al2006; @RevellHarmon2008; @Beaulieu_et_al2012; @Adams2014b; @Adams2014a; @AdamsCollyer2018b]. These methods are predicated on the notion that phylogenetic signal -- the tendancy for closely related species to display similar trait values -- is present in cross-species datasets [@Felsenstein1985; @Pagel1999; @Blomberg_et_al2003]. Indeed, under numerous evolutionary models, phylogenetic signal is to be expected, as stochastic character change along the hierarchical structure of the tree of life generates trait covaration among related taxa [see @Felsenstein1985; @Blomberg_et_al2003; @Revell_et_al2008]. \hfill\break

Several analytical tools have been developed to quantify phylogenetic signal in phenotypic datasets, including measures of serial independence [$\mathbf{C}$: @Abouheif1999], autocorrelation estimates [$I$: @Gittleman1990], statistical ratios of trait variation relative to what is expected given the phylogeny [$Kappa$: @Blomberg_et_al2003; @Adams2014a], and scaling parameters used in maximum likelihood fitting of the data to the phylogeny [$\lambda$: @Pagel1999], among others [e.g., @Klingenberg2010]. The statistical properties of these methods -- namely type I error rates and power -- have also been investigated to determine when phylogenetic signal can be detected and under what conditions [e.g., @Munkemuller_et_al2012; @Pavoine2012;  @DinizFilho2012; @Adams2014a; @MolinaVenegas2017; see also @Revell_et_al2008; @Revell2010]. One of the most widely used methods for characterizing phylogenetic signal in macroevolutionary studies is Pagel's $\lambda$ [@Pagel1999]. Here, maximum likelihood is used to fit the data to the phylogeny under a Brownian motion model of evolution. A parameter ($\lambda$) is included, which transforms the lengths of the internal branches of the phylogeny to improve the fit [@Pagel1999; @Freckleton_et_al2002]. Pagel's $\lambda$ ranges from $0\to1$, with larger values signifying a greater dependence of observed trait variation on the phylogeny. Pagel's $\lambda$ also has the appeal that it may be included in phylogenetic regression  (PGLS) to account for the degree of phylogenetic signal in comparative analyses [see @Freckleton_et_al2002]. \hfill\break

Evolutionary biologists commonly seek to describe the relative strength of phylogenetic signal in phenotypic traits, to determine the extent to which shared evolutionary history has influenced trait covariation among taxa. This is often accomplished by interpreting empirical estimates of $\lambda$; with smaller values signifying 'weak' phylogenetic signal, while larger values are interpreted as 'strong' phylogenetic signal [e.g., @DeMeester2019; @Pintanel2019;@Su2019]. Other approaches for interpreting $\lambda$ are more statistical. For instance, some have evaluated whether the observed $\lambda$ differs from some expected value through the use of confidence intervals [@Vandelook2019] or by performing likelihood ratio tests that compare the observed model fit to that obtained when $\lambda=0$ or $\lambda=1$ [@Freckleton_et_al2002; @Cooper2010; @Bose2019]. Additionally, qualitative comparisons of $\lambda$ estimates obtained from multiple phenotypic traits have been used to infer whether the strength of phylogenetic signal is greater in one trait as compared to another [e.g., @Liu2019; @Bai2019]. Indeed, statements regarding the strength of phylogenetic signal based on $\lambda$ are rather common in the evolutionary literature. For instance, of the 204 papers published in 2019 that estimated and reported Pagel's $\lambda$ (found from a literature survey we conducted in Google.scholar), 40% interpreted the strength of phylogenetic signal for at least one phenotypic trait. Further, because nearly half of the 1,572 $\lambda$ values reported were near 0 or 1 (Figure 1) where the biological interpretation of $\lambda$ is known, this percentage is even higher.

@@

@@

Second, while estimates of $\lambda$ are within a bounded scale ($0\to1$), this does not *de-facto* imply that the estimated values of this parameter correspond to the actual strength of the underlying input signal in the data. For this to be the case, $\lambda$ must be a statistical effect size. Effect sizes are a measure of the magnitude of a statistical effect in data, represented on a common scale [@Glass1976; @Cohen1988]. Effect sizes have widespread use in many areas of the quantiative sciences, as they represent measures that may be readily summarized across datasets as in meta-analyses [@HedgesOlkin1985; @Glass1976; @Arnqvist1995], or compared among datasets [e.g., @AdamsCollyer2016; @AdamsCollyer2019b]. Unfortunatley, not all model parameters and test statistics are effect sizes, and thus many summary measures must first be converted to standardized units (i.e., an effect size) for meaningful comparison [see @Rosenthal1994]. As a consequence, it follows that only if $\lambda$ is a statistical effect size can comparisons of estimates across datasets be interpretable. For the case of $\lambda$, this has not yet been explored.  \hfill\break

@@

@@

To evaluate the utility of $Z_K$ and $Z_\lambda$ we calculated both effect sizes for the simulated datasets generated above, and summarized the precision of each using its variance ($\sigma^2_{Z_K}$ and $\sigma^2_{Z_\lambda}$, Figure 4: additional results in the Supporting Information). Here two things are evident. First, estimates of $Z_K$ linearly track the input phylogenetic signal whereas estimates of $Z_\lambda$ do not (Figure 4A,B). Thus, actual changes in the strength of phylogenetic signal are reflected more evenly in the corresponding values of the effect size $Z_K$. Second, the precision of $Z_K$ is considerably more stable as compared with $Z_\lambda$. This may be seen by calculating the coefficients of variation for the set of precision estimates (i.e., $\sigma^2_{Z_K}$ and $\sigma^2_{Z_\lambda}$) across input levels of phylogenetic signal.  Here coefficients of variation in the precision of $Z_K$ were up to an order of magnitude smaller for than for $Z_\lambda$ (Figure 4C), implying that estimates of the strength of phylogenetic signal were more reliable and robust when using $Z_K$. \hfill\break

@@

\begin{align}
  \hat{Z}_{12}=\frac{\lvert{(K_{1}-\hat\mu_{K_1})-(K_{2}-\hat\mu_{K_2})}\rvert}{\sqrt{\hat\sigma^2_{K_1}+\hat\sigma^2_{K_2}}}
\end{align}

where $K_1$, $K_2$, $\hat\mu_{K_1}$, $\hat\mu_{K_2}$, $\hat\sigma_{K_1}$, and $\hat\sigma_{K_2}$ are as defined above for equation 2. Estimates of significance of $\hat{Z}_{12}$ may be obtained from a standard normal distribution. Typically, $\hat{Z}_{12}$ is considered a two-tailed test, however directional (one-tailed) tests may be specified should the empirical situation require it [see @AdamsCollyer2016; @AdamsCollyer2019b]. \hfill\break

@@

As an alternative, we described a standardized effect size ($Z$) for assessing the strength of phylogenetic signal. $Z$ expresses the magnitude of phylogenetic signal as a standard normal deviate, which is easily interpretable as the strength of phylogenetic signal relative to the mean. We applied this concept to both $\lambda$ and $Kappa$, and found that $Z_K$ was a better estimate of the strength of phylogenetic signal in phenotypic data. First, $Z_K$ was more precise than $Z_{\lambda}$, and variation in this precision was more consistent across the range of input levels of phylogenetic signal. Additionally, values of $Z_K$ more accurately tracked known levels of phylogenetic signal, with changes in the actual strength of phylogenetic signal reflected in a more linear fashion by concomitant changes in the values of $Z_K$. Thus, $Z_K$ holds promise as a measure of the relative strength of phylogenetic signal that reflects the magnitude of this effect in phenotypic data. We therefore recommend that future studies interested in the strength of phylogenetic signal incorporate $Z_K$ as a statistical measure of this effect. \hfill\break

Based on the effect size $Z_K$, we then proposed a two-sample test, which provides a statistical means of determining whether the strength of phylogenetic signal is greater in one phenotypic trait as compared to another. Prior studies have summarized patterns of variation in phylogenetic signal across datasets using summary test values, such as $Kappa$ [e.g.,  @Blomberg_et_al2003]. However, $Kappa$ does not scale linearly with input levels of phylogenetic signal, and its variance increases (i.e., precision decreases) with increasing strength of phylogenetic signal [@Munkemuller_et_al2012; @DinizFilho2012: see also Supporting Information]. Thus, $Kappa$ should not be considered a standardized effect size that measures the strength of phylogenetic signal on a common scale. By contrast, converting $Kappa$ to $Z_K$ (via equation 2) alleviates these concerns, and facilitates formal statistical comparisons of the strength of signal across datasets. Thus when viewed from this perspective, the approach developed here aligns well with other statistical approaches such as meta-analysis [sensu @HedgesOlkin1985; @Glass1976; @Arnqvist1995], where summary statistics across datasets are converted to standardized effect sizes for subsequent 'higher order' statistical summaries or comparisons. As such our approach enables evolutionary biologists to quantitatively examine the relative strength of phylogenetic signal across a wide range of phenotypic traits, and thus opens the door for future discoveries that inform on how phenotypic diversity accumulates in macroevolutionary time across the tree of life.  \hfill\break

One important advantage of the approach advocated here is that the resulting effect sizes ($Z_K$) are dimensionless, as the units of measurement cancel out during the calculation of $Z$ [@SokalRohlf2012]. Thus, $Z_K$ represents the strength of phylogenetic signal on a common and comparable scale -- measured in standard deviation units -- regardless of the initial units and original scale of the phenotypic variables under investigation. This means that the strength of phylogenetic signal may be compared across datsets for continuous phenotypic traits measured in different units and scale, because those units have been standardized through their conversion to $Z_K$. For example, our approach could be utilized to determine whether the strength of phylogenetic signal (say, in response to ecological differentiation) is stronger in morphological traits (linear traits: $mm$), physiological traits (metabolic rate: $\frac{O^2}{min}$), or behavioral traits (aggression: $\frac{\#{displays}}{second}$). In fact, our empirical example provided such a comparison, as SA:V is represented in $mm^{-1}$ while relative body size is a unitless ratio ($\frac{BW}{SVL}$). Additionally, our method  is capable of comparing the strength of phylogenetic signal in traits of different dimensionality, as estimates of phylogenetic signal using $Kappa$ have been generalized for multivariate data [$K_{mult}$: see @Adams2014a]. Furthermore, tests based on $\hat{Z}_{12}$ may be utilized for comparing the strength of phylogenetic signal among datasets containing a different number of species, and even for phenotypes obtained from species in different lineages, because their phylogenetic non-independence and observed variation are taken into account in the generation of the empirical sampling distribution via permutation.    \hfill\break

**Finally... Need Closing paragraph.**

>>>>

Macroevolutionary studies frequently characterize the phylogenetic signal in phenotypes, and wish to compare the strength of that signal across traits. However, analytical tools for such comparisons have largely remained underdeveloped. In this study, we evaluated the efficacy of one commonly used parameter (Pagel's $\lambda$) to estimate the strength of phylogenetic signal in phenotypic traits, and evaluate the degree to which $\lambda$ correctly identifies known levels of phylogenetic signal. We find that the precision of $\lambda$ in estimating actual levels of phylogenetic signal is often inaccurate, and that biological interpretations of the strength of phylogenetic signal based on $\lambda$ are therefore compromised. We then propose a standardized effect size based on $Kappa$ ($Z_K$), which measures the strength of phylogenetic signal, and places it on a common scale for statistical comparison. Tests based on $Z_K$ provide a mechanism for formally comparing the strength of phylogenetic signal across datasets, in much the same manner as effect sizes may be used to summarize patterns in quantitative meta-analysis. Our approach extends the phylogenetic comparative toolkit to address hypotheses that compare the strength of phylogenetic signal between various phenotypic traits, even when those traits are found in different evolutionary lineages or have different units or scale.

@@

# Introduction
Investigating macroevolutionary patterns of trait variation requires a phylogenetic perspective, because the shared ancestry among species violates an assumption of independence among trait valuesthat is common for statistical tests [@Felsenstein1985; @HarveyPagel1991]. Accounting for this evolutionary non-independence is the purview of *phylogenetic comparative methods* (PCMs): a suite of analytical tools that condition trends in the data on the phylogenetic relatedness of observations [e.g., @Grafen1989; @GarlandIves2000; @Rohlf2001; @ButlerKing2004]. The past several decades have witnessed a rapid expansion in the development of PCMs to address an ever-growing set of macroevolutionary hypotheses [@MartinsHansen1997; @OMeara_et_al2006; @RevellHarmon2008; @Beaulieu_et_al2012; @Adams2014b; @Adams2014a; @AdamsCollyer2018b]. These methods are predicated on the notion that phylogenetic signal -- the tendancy for closely related species to display similar trait values -- is present in cross-species datasets [@Felsenstein1985; @Pagel1999; @Blomberg_et_al2003]. Indeed, under numerous evolutionary models, phylogenetic signal is to be expected, as stochastic character change along the hierarchical structure of the tree of life generates trait covaration among related taxa [see @Felsenstein1985; @Blomberg_et_al2003; @Revell_et_al2008]. \hfill\break

Several analytical tools have been developed to quantify phylogenetic signal in phenotypic datasets, including measures of serial independence [$\mathbf{C}$: @Abouheif1999], autocorrelation estimates [$I$: @Gittleman1990], statistical ratios of trait variation relative to what is expected given the phylogeny [$Kappa$: @Blomberg_et_al2003; @Adams2014a], and scaling parameters used in maximum likelihood fitting of the data to the phylogeny [$\lambda$: @Pagel1999], among others [e.g., @Klingenberg2010]. The statistical properties of these methods -- namely type I error rates and power -- have also been investigated to determine when phylogenetic signal can be detected and under what conditions [e.g., @Munkemuller_et_al2012; @Pavoine2012;  @DinizFilho2012; @Adams2014a; @MolinaVenegas2017; see also @Revell_et_al2008; @Revell2010]. One of the most widely used methods for characterizing phylogenetic signal in macroevolutionary studies is Pagel's $\lambda$ [@Pagel1999]. The ($\lambda$) parameter stransforms the lengths of the internal branches of the phylogeny to improve a fit of data to the phylogeny via maximum likelihood [@Pagel1999; @Freckleton_et_al2002]. Pagel's $\lambda$ ranges from $0\to1$, with larger values signifying a greater dependence of observed trait variation on the phylogeny. Pagel's $\lambda$ also has the appeal that it may be included in phylogenetic generalized least-squares regression (PGLS) to account for the degree of phylogenetic signal in comparative analyses [see @Freckleton_et_al2002]. \hfill\break

In addition to functioning as a parameter that is tuned for appropriate analysis, $\lambda$ can function as a descriptive statistic to describe the relative strength of phylogentic signal in phenotypic traits, to determine the extent to which shared evolutionary history has influenced trait covariation among taxa. The appeal of $\lambda$ as a descriptive statistic for evolutionary biologists is a basis for interpreting "weak" versus "strong" phylogenetic signal; i.e., small versus large values of $\lambda$, respectively, in a comparative sense [e.g., @DeMeester2019; @Pintanel2019;@Su2019]. Indeed, statements regarding the strength of phylogenetic signal based on $\lambda$ are rather common in the evolutionary literature. For instance, of the 204 papers published in 2019 that estimated and reported Pagel's $\lambda$ (found from a literature survey we conducted in Google.scholar), 40% interpreted the strength of phylogenetic signal for at least one phenotypic trait. Further, because nearly half of the 1,572 $\lambda$ values reported were near 0 or 1 (Figure 1) where the biological interpretation of $\lambda$ is known, this percentage is even higher. \hfill\break

@@

Various other approaches use $\lambda$ as a parameter that can be varied for inferences akin to sensitivty analysis. For instance, some have performed likelihood ratio tests that compare observed model fits to those obtained when $\lambda=0$ or $\lambda=1$ [@Freckleton_et_al2002; @Cooper2010; @Bose2019] or evaluated whether observed $\lambda$ differs from an expected $\lambda$, based on confidence intervals generated for the expected value [@Vandelook2019].  Qualitative comparisons of $\lambda$ estimates have also been performed for multiple traits on the same phylogenetic tree to infer whether the strength of phylogenetic signal is greater in one trait as compared to another [e.g., @Liu2019; @Bai2019].

@@

Second, while estimates of $\lambda$ are within a bounded scale ($0\to1$), this does not *de-facto* imply that the estimated values of this parameter correspond to the actual strength of the underlying input signal in the data. For this to be the case, $\lambda$ must be a statistical effect size. Effect sizes are a measure of the magnitude of a statistical effect in data, represented on a common scale [@Glass1976; @Cohen1988]. Effect sizes have widespread use in many areas of the quantiative sciences, as they represent measures that may be readily summarized across datasets as in meta-analyses [@HedgesOlkin1985; @Glass1976; @Arnqvist1995], or compared among datasets [e.g., @AdamsCollyer2016; @AdamsCollyer2019b]. Unfortunatley, not all model parameters and descriptive statistics are effect sizes, and thus many summary measures must first be converted to statistics with standardized units (i.e., conversion to an effect size) for meaningful comparison [see @Rosenthal1994]. As a consequence, it follows that only if $\lambda$ is a statistical effect size can comparisons of estimates across datasets be interpretable. For the case of $\lambda$, this has not yet been explored.  \hfill\break

@@

***note from Mike***  Throughout the ms thus far $Kappa$ is used.  Why not $\kappa$, the actual greek symbol for $Kappa$?

@@

To evaluate the utility of $Z_K$ and $Z_\lambda$ we calculated both effect sizes for the simulated datasets generated above, and summarized the precision of each using its variance ($\sigma^2_{Z_K}$ and $\sigma^2_{Z_\lambda}$, Figure 4: additional results in the Supporting Information). Here two things are evident. First, estimates of $Z_K$ linearly track the input phylogenetic signal whereas estimates of $Z_\lambda$ do not (Figure 4A, B). Thus, actual changes in the strength of phylogenetic signal are reflected more evenly in the corresponding values of the effect size $Z_K$. Second, the precision of $Z_K$ is considerably more stable as compared with $Z_\lambda$. This may be seen by calculating the coefficients of variation for the set of precision estimates (i.e., $\sigma^2_{Z_K}$ and $\sigma^2_{Z_\lambda}$) across input levels of phylogenetic signal.  Coefficients of variation in the precision of $Z_K$ were up to an order of magnitude smaller for than for $Z_\lambda$ (Figure 4C), implying that estimates of the strength of phylogenetic signal were more reliable and robust when using $Z_K$. \hfill\break

@@

\begin{align}
  \hat{Z}_{12}=\frac{\lvert{(K_{1}-\hat\mu_{K_1})-(K_{2}-\hat\mu_{K_2})}\rvert}{\sqrt{\hat\sigma^2_{K_1}+\hat\sigma^2_{K_2}}} = \frac{\lvert Z_{K_1} - Z_{K_2}\rvert}{\sqrt{2}}
\end{align}

where $K_1$, $K_2$, $\hat\mu_{K_1}$, $\hat\mu_{K_2}$, $\hat\sigma_{K_1}$, and $\hat\sigma_{K_2}$ are as defined above for equation 2. The right side of the equation illustrates that if $Z_K$ has already been calculated for two sampling distributions as in equation 2, the sampling distributions have unit variance for each of the $Z_K$ statistics.  Estimates of significance of $\hat{Z}_{12}$ may be obtained from a standard normal distribution. Typically, $\hat{Z}_{12}$ is considered a two-tailed test, however directional (one-tailed) tests may be specified should the empirical situation require it [see @AdamsCollyer2016; @AdamsCollyer2019b]. \hfill\break

@@

As an alternative, we described a standardized effect size ($Z$) for assessing the strength of phylogenetic signal. $Z$ expresses the magnitude of phylogenetic signal as a standard normal deviate, which is easily interpretable as the strength of phylogenetic signal relative to the mean. We applied this concept to both $\lambda$ and $Kappa$, and found that $Z_K$ was a better estimate of the strength of phylogenetic signal in phenotypic data. First, $Z_K$ was more precise than $Z_{\lambda}$, and precision was more consistent across the range of input levels of phylogenetic signal. Additionally, values of $Z_K$ more accurately tracked known levels of phylogenetic signal, with changes in the actual strength of phylogenetic signal reflected in a more linear fashion by concomitant changes in the values of $Z_K$. Thus, $Z_K$ holds promise as a measure of the relative strength of phylogenetic signal that reflects the magnitude of this effect in phenotypic data. We therefore recommend that future studies interested in the strength of phylogenetic signal incorporate $Z_K$ as a statistical measure of this effect. \hfill\break

Based on the effect size $Z_K$, we then proposed a two-sample test, which provides means of determining whether the strength of phylogenetic signal is greater in one phenotypic trait as compared to another, via a hypothesis test. Prior studies have summarized patterns of variation in phylogenetic signal across datasets using summary test values, such as $Kappa$ [e.g.,  @Blomberg_et_al2003]. However, $Kappa$ does not scale linearly with input levels of phylogenetic signal, and its variance increases (i.e., precision decreases) with increasing strength of phylogenetic signal [@Munkemuller_et_al2012; @DinizFilho2012: see also Supporting Information]. Thus, $Kappa$ should not be considered an effect size that measures the strength of phylogenetic signal on a common scale. By contrast, standardizing $Kappa$ ($Z_K$, via equation 2) alleviates these concerns, and facilitates formal statistical comparisons of the strength of signal across datasets. Thus when viewed from this perspective, the approach developed here aligns well with other statistical approaches such as meta-analysis [sensu @HedgesOlkin1985; @Glass1976; @Arnqvist1995], where summary statistics across datasets are converted to standardized effect sizes for subsequent "higher order" statistical summaries or comparisons. As such our approach enables evolutionary biologists to quantitatively examine the relative strength of phylogenetic signal across a wide range of phenotypic traits, and thus opens the door for future discoveries that inform on how phenotypic diversity accumulates in macroevolutionary time across the tree of life.  \hfill\break

One important advantage of the approach advocated here is that the resulting effect sizes ($Z_K$) are dimensionless, as the units of measurement cancel out during the calculation of $Z$ [@SokalRohlf2012]. Thus, $Z_K$ represents the strength of phylogenetic signal on a common and comparable scale -- measured in standard deviation -- regardless of the initial units and original scale of the phenotypic variables under investigation. This means that the strength of phylogenetic signal may be compared across datsets for continuous phenotypic traits measured in different units and scale, because those units have been standardized through their conversion to $Z_K$. For example, our approach could be utilized to determine whether the strength of phylogenetic signal (say, in response to ecological differentiation) is stronger in morphological traits (linear traits: $mm$), physiological traits (metabolic rate: $\frac{O^2}{min}$), or behavioral traits (aggression: $\frac{\#{displays}}{second}$). In fact, our empirical example provided such a comparison, as SA:V is represented in $mm^{-1}$ while relative body size is a unitless ratio ($\frac{BW}{SVL}$). Additionally, our method  is capable of comparing the strength of phylogenetic signal in traits of different dimensionality, as estimates of phylogenetic signal using $Kappa$ have been generalized for multivariate data [$K_{mult}$: see @Adams2014a]. Furthermore, tests based on $\hat{Z}_{12}$ may be utilized for comparing the strength of phylogenetic signal among datasets containing a different number of species, and even for phenotypes obtained from species in different lineages, because their phylogenetic non-independence and observed variation are taken into account in the generation of the empirical sampling distribution via permutation.    \hfill\break

Phylogenetic signal can be thought of as both an attribute to be measured in the data and a paramter that can be tuned to account for the phylogenetic non-independence among observations, for analysis of the data.  As such, $\lambda$ is appealing, as a statistic that potentially fulfills both roles.  However, the inability to estimate phylogenetic signal with $\lambda$ for data simulated with known phylogenetic signal is troublesome, and we recommend evolutionary biologists refrain from viewing it as a useful  statistic to describe the amount of phylogenetic signal in the data.  Interestingly, $Kappa$ is a better statistic for measuring the amount of phylogenetic signal in data simulated with respect to known levels of $\lambda$.  Although $\lambda$ might be viewed as an important parameter for modifying the the conditional estimation of linear model coefficients with respect to phylogeny, it is neither a statistic that has meaningful comparative value as a measure of phylogenetic signal nor a statistic that lends itself well to reliable calculation of a test statistic.  By contrast, $Kappa$ has been shown here to be a reliable statistic, but only when standardized by the mean and standard deviation of its empirical sampling distribution.  Because one has control over the number of permutations used in analysis, one can be assured with many permutations that the empirical sampling distribution is representative of true probability distributions [@AdamsCollyer2018b].  With low coefficients of variation for $Z_K$ (Figure 4), it is difficult to imagine that a hypothesis test can improve equation 4 for efficiently comparing phylogenetic signal for different traits, different trees, or a combination of both.
